---
title: "Cond probability"
author: "Dr K"
date: "February 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is chance that you pick 3 people at random and get exactly one unemployed. We assume an unemployment rate of .079

Our approach will be to create a pseudo population with 10000 people in it. We will use numbers - 0 for employed and 1 for unemployed.  

Put our numbers in something -- call it bucket

```{r}
unemp = rep(1,times=790)
employ= rep(0,10000-790)
peepl=c(unemp,employ)
```

Now we going to start picking out groups of 3 and see how often we get jus one unemployed.

Plan is to make some code that goes in a loop.  

```{r}
results=numeric()
for (i in 1:5000){
  onsamp = sample(peepl,size=3,replace = T)
  results[i]=sum(onsamp)
}
table(results)
```

How can we modify this to answer what is probability of 2 out of 8 ?  Compare with Mine's video on2 out of 8.

```{r}
results=numeric()
for (i in 1:5000){
  onsamp = sample(peepl,size=8,replace = T)
  results[i]=sum(onsamp)
}
table(results)
```